A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-17 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{We have replaced ``However, CNN attacks are usually expected imperceptible but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.'' with}
``\uline{However, CNN attacks are usually expected imperceptibly but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have  replaced ``$A_add$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.'' with}
``\uline{$A_{add}$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.}''
\textbf{in Section III.B of the revised manuscript.}

\textbf{We have replaced ``We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{LaSOT}, UAV123 \cite{UAV123}, VOT1016 \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}.'' with}
``\uline{We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{LaSOT}, UAV123 \cite{UAV123}, VOT2016 \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}.}''
\textbf{in Section IV.A of the revised manuscript.}

\textbf{We have replaced ``We adopt COCO \cite{COCO}, ILSVRC-VID \cite{VID} and the training splits of GOT-10k \cite{GOT-10k} and LaSOT \cite{LaSOT} as our training set. (see Table I)'' with}
``\uline{We adopt COCO \cite{COCO}, ILSVRC-VID \cite{VID} and the training splits of GOT-10k \cite{GOT-10k} and LaSOT \cite{LaSOT} as our training set.}''
\textbf{in Section IV.B of the revised manuscript.}

@@

Thank you very much for your thorough review. Your insightful comments are very helpful for us to improve the quality of the paper. According to your comments and suggestions, we have carefully and extensively revised the manuscript. The main revised parts are highlighted by underlines in the underlined version for your convenience. You will find that all your comments and suggestions are considered and followed. We hope that our revised manuscript is now appropriate for publication in IEEE Transactions on Circuits and Systems for Video Technology.
In addition, point-to-point responses to your comments are given below and highlighted using bold font in line with your comments in order to facilitate cross-referencing.\\[10pt]
\indent We are looking forward to your reply.\\[10pt]
\noindent Yours sincerely,\\
\noindent Zhenbang Li, Yaya Shi, Jin Gao, Shaoru Wang, Bing Li, Pengpeng Liang, Weiming Hu
\\
\\
\\
\noindent Dr. Jin Gao (Contact author)\\
\noindent National Laboratory of Pattern Recognition (NLPR)\\
\noindent Institute of Automation, Chinese Academy of Sciences (CASIA)\\
\noindent Address: No. 95, Zhongguancun East Road, Haidian District,\\
\noindent Beijing 100190, P. R. China\\
\noindent Email: jin.gao@nlpr.ia.ac.cn

\newpage

%%%% 问题 3.1 %%%%
\textit{This paper employs the universal perturbation attacks on Siamese visual trackers. There are still the following concerns about the proposed method. 1. As stated in the paper, the proposed method ``does not require gradient optimization or network inference". However, this is a double-edged sword since it resulted in suspicious attacks. Prior works commonly train a network to prevent not only suspicious attacks but also modifying every pixel. I think it's a major problem with this work. I suggest considering a proper strategy to remove/reduce it.}

\textbf{
Thanks for your advice.
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在$64 \times 64$这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64 \times 64$, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are least sensitive that the Y channel. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The detailed analysis of new added experiment is added in Section IV.D of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

@@

\begin{table}[t]
  \centering
  \caption{Influence of different ways to perturb the search image. One way is adding a small patch on the RGB channel. The other way is adding perturbation on the whole search image on the Y channel and add a small patch on the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:perturb}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  GRB Attack                                             & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}

\uline{\textit{Ablation Study: Attack in YCbCr Space}
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在$64 \times 64$这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64 \times 64$, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add the perturbation over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel.%The perturbed search image is then converted into RGB color space and fed into the tracking network.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are least sensitive that the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
% 介绍模板图像
For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels.
The perturbed template and search images are then converted into RGB color scpace and fed into the tracking network.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
The other steps of the training process are the same as the attack method in Section III.
% 实验结果。
The experimental result is shown in Table \ref{table:perturb}. As we can see,
% 分析攻击性能
the attack performance is slightly degraded. In terms of AO on GOT-VAL, the targeted attack performance changes from 0.840 to 0.680, and the untargeted attack performance changes from 0.153 to 0.246.
% 分析可感知性
% As shown in Figure \ref{fig:YCbCr}, 
As shown in Table \ref{table:perturb},
our new method can increase SSIM of the search image from 0.56 to 0.78. The template SSIM remains unchanged at 0.79.
}

### 2021-09-17 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
改response

\begin{table}[t]
  \centering
  \caption{Influence of different ways to perturb the search image. One way is adding a small patch on the RGB channel. The other way is adding perturbation on the whole search image on the Y channel and add a small patch on the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:pertrub}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  GRB Attack                                             & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}
\uline{\textit{Ablation Study: Attack in YCbCr Space}
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在64*64这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of 64*64, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while having a targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of 64*64 in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are least sensitive that the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The experimental result is shown in Table \ref{table:pertrub}. As we can see,
% 分析攻击性能
the attack performance is slightly degraded. In terms of AO on GOT-VAL, the targeted attack performance changes from 0.840 to 0.680, and the untargeted attack performance changes from 0.153 to 0.246.
% 分析可感知性
As shown in Figure \ref{fig:YCbCr}, our new method can increase SSIM of the search image from 0.56 to 0.78. The template SSIM remains unchanged at 0.79.
}

>>>>

\begin{table}[t]
  \centering
  \caption{Influence of different ways to perturb the search image. One way is adding a small patch on the RGB channel. The other way is adding perturbation on the whole search image on the Y channel and add a small patch on the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:pertrub}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  GRB Attack                                             & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}
\uline{\textit{Ablation Study: Attack in YCbCr Space}
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在64*64这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64\times 64$, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are least sensitive that the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The experimental result is shown in Table \ref{table:pertrub}. As we can see,
% 分析攻击性能
the attack performance is slightly degraded. In terms of AO on GOT-VAL, the targeted attack performance changes from 0.840 to 0.680, and the untargeted attack performance changes from 0.153 to 0.246.
% 分析可感知性
As shown in Figure \ref{fig:YCbCr}, our new method can increase SSIM of the search image from 0.56 to 0.78. The template SSIM remains unchanged at 0.79.
}
